SHARP II: Dark Matter Substructure, Gravitational Lens flux-ratio Anomalies, and the Case of B1555+375: Beware the Effect of Edge-on Disks

### 2015-08-17 papers/B1555_EdgeOn/B1555_letter.tex
minor update to draft

It was first suggested by \citet{Mao1998} that flux-ratio anomalies
observed in radio-loud multiple images of lensed quasars could be
interpreted as a telltale sign of the presence of substructure in lens
galaxies.  Indeed, small perturbations in the gravitational potential
are sufficient to cause flux-ratio anomalies in strong lensed systems
\citep{Bradac02}.  Moreover, unlike in the optical or infrared, in the
radio band, lensed images are neither sensitive to microlensing from
stars, nor to dust extinction. This makes flux-ratio anomalies a promising
tool to detect \textbf{and measure} dark matter substructures \citep{Dalal2002,N13}.  
%At present, the amount of substructure derived from flux-ratio anomalies
%seems to be disagreement with predictions from numerical simulations, 
%with the former requiring a larger fraction of mass in substructure than
%expected \citep{Xu14}. 
\textbf{At present, the amount of substructure derived from flux-ratio anomalies ease the disagremeent with direct-detections and numerical simulations, with the less level of flux anomalies showing in simulation results \citep{Xu14}.}
While this could be the result of small sample
statistics, it could also be an indication that flux-ratio anomalies
have a different origin than substructure.[OTHER POSSIBLE ORIGONS--SIMONA]
%
An alternative method for
the detection of substructure in gravitational lens galaxies, utilizing
the surface brightness distribution of extended arcs and Einstein rings
has been introduced by \citet{K05} and \citet{V09}. Interestingly, the fraction of
substructure measured with this \emph{gravitational imaging technique}
is currently in agreement with theoretical expectations \citep{V14a,V12}, \textbf{although the number of detections remains small}.

>>>>

It was first suggested by \citet{Mao1998} that flux-ratio anomalies
observed in radio-loud multiple images of lensed quasars could be
interpreted as a telltale sign of the presence of substructure in lens
galaxies.  Indeed, small perturbations in the gravitational potential
are sufficient to cause flux-ratio anomalies in strong lensed systems
\citep{Bradac02}.  Moreover, unlike in the optical or infrared, in the
radio band, lensed images are neither sensitive to microlensing from
stars, nor to dust extinction. This makes flux-ratio anomalies a promising
tool to detect \textbf{and measure} dark matter substructures \citep{Dalal2002,N13}.  
%At present, the amount of substructure derived from flux-ratio anomalies
%seems to be disagreement with predictions from numerical simulations, 
%with the former requiring a larger fraction of mass in substructure than
%expected \citep{Xu14}. 
\textbf{At present, the amount of substructure derived from flux-ratio anomalies ease the disagremeent with direct-detections and numerical simulations.
Utilizing the surface brightness distribution of extended arcs and Einstein rings
has been introduced by \citet{K05} and \citet{V09}. The fraction of
substructure measured with this \emph{gravitational imaging technique}
is currently in agreement with theoretical expectations \citep{V14a,V12}, although the simulation results show less level of flux anomalies than expected \citep{Xu14}.}
While this could be the result of small sample
statistics, it could also be an indication that flux-ratio anomalies
have a different origin than substructure. \textbf{ISM and microlensing both can produce flux anomalies in lens systems, but the effects from ISM show strong frequency dependence and observing in radio band can avoid microlensing from star-size objects \citep{KD04}. These origins are ruled out among known radio loud flux anomlous systems support the detection of substructures. }[OTHER POSSIBLE ORIGONS--SIMONA]
%
